---
title: "The Ramen Rater"
author: "Kenneth Daily"
date: "February 7, 2018"
output: html_document
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)

library(synapser)
library(tidyverse)
library(ggplot2)
library(viridis)

syn <- synLogin()
```

## Introduction

I was created by running:

```{r}
library(githubr)

# Get remote github repository for this file
repo <- getRepo("kdaily/20180212-hbgdki-rally-6-kickoff")

# Get current path to version at latest commit
thisFile <- getPermlink(repo, "ramen.Rmd")
```

This above snippet has some procedural issues that must be followed - namely, the local file and the remote Github file must be identical, so a push to Github must be performed before this file is rendered as below.

```
synapser::synLogin()
knit2synapse::knitfile2synapse("./ramen.Rmd", owner="syn11801878")
```

## Get some data

Get the data from The [Ramen Rater](https://www.theramenrater.com/resources-2/the-list/) to summarize.

```{r readramen}
ramenUrl <- "https://gist.githubusercontent.com/kdaily/c5b40ed3821090e876b02f0fd733e927/raw/34f40712a63f0849a940a62042c0c499fc3afb46/The-Ramen-Rater-The-Big-List.csv"

data <- readr::read_csv(ramenUrl)
```

## Summarize

Do a basic summary and save the resulting file to Synapse. Multiple runs of this will version this file, if the content (hence, the md5) changes. Note the provenance is set using files external to Synapse, including the original remote CSV file, and the most recent commit in Github of this Markdown file. 

```{r summarize, message=FALSE, warning=FALSE, echo=TRUE}
dataSummary <- data %>% count(Style) %>%
  mutate(Style=forcats::fct_reorder(factor(Style), n))

readr::write_csv(dataSummary, path="/tmp/ramen-summary.csv")

folder <- synStore(Folder("ramen-example", parent="syn11801621"))
summaryFile <- File("/tmp/ramen-summary.csv", parent=folder)
summaryFile <- synStore(summaryFile, used=ramenUrl, executed=thisFile)
```

### Summary table

```{r}
dataSummary %>% arrange(desc(n)) %>% knitr::kable()
```

### A plot

This image is added to the Wiki as a "Wiki attachment".

```{r plot, echo=FALSE}
p <- ggplot(dataSummary, aes(x=Style, y=n))
p <- p + geom_col()
p <- p + theme_bw()
p
```

```{r}
sessionInfo()
```

